---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# DFR JASA Discussion

This repository contains the LaTeX source for a JASA discussion/commentary on
Deep Frechet Regression, along with the code and figures used for the manifold
dimension selection example.

## Repository Layout

- `jasa-manuscript.tex`: main JASA manuscript file.
- `manuscript/`: section-level manuscript source files.
- `references.bib`: bibliography database.
- `agsm.bst`: bibliography style used by the JASA template.
- `figures/`: figure files included in the manuscript.
- `code/manifold-selection-example.R`: R script used to generate the simulation
  figures.
- `preprint-manuscript.tex`: earlier preprint manuscript source, kept for
  reference.

## Build Locally

The manuscript is built with `pdflatex` and BibTeX through `latexmk`.

```sh
make
```

or explicitly:

```sh
make pdf
```

The output is `jasa-manuscript.pdf`.

To remove LaTeX auxiliary files:

```sh
make clean
```

To also remove the generated PDF and log:

```sh
make cleanall
```

## Regenerate Figures

The figures can be regenerated from the R script:

```sh
make figures
```

This requires the R packages used by `code/manifold-selection-example.R`,
including `ggplot2`, `lattice`, `data.table`, `scales`, `sn`, `here`, and any
other packages loaded by the script.

## Overleaf Notes

For Overleaf, upload the source files rather than local build products. The
important files are:

- `jasa-manuscript.tex`
- `manuscript/`
- `references.bib`
- `agsm.bst`
- `figures/`

Use `jasa-manuscript.tex` as the main document, `pdfLaTeX` as the compiler, and
BibTeX for the bibliography. If switching from an older `biblatex` version,
clear cached/generated files or use "Recompile from scratch" so stale
`*.aux`/`*.bbl` files do not interfere with the natbib build.

## Generated Files

LaTeX build products such as `*.aux`, `*.bbl`, `*.blg`, `*.fdb_latexmk`,
`*.fls`, `*.out`, and `*.synctex.gz` are ignored by Git. The PDF and log are
also ignored locally.

## Acknowledgement

Edward Gunning is the author of this repository. 
The author used ChatGPT Version 5.5 (OpenAI) for coding and copy-editing assistance.
It was also used to help versioning the repository and construct the README and Makefile.
All AI generated edits were reviewed and approved by the author.

### Reproducibility Notes

```{r}
sessionInfo()
```

